---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# goggles

> Spreadsheets are dangerous.  Wear goggles.

> `Goggles` help(s) you spot spreadsheet anomalies in the wild.

Spreadsheets are notoriously helpful in converting numbers to dates.  Humans are
notoriously unhelpful in overwriting formulas with literals.  With goggles, you
can quickly visualise possible errors.

This is basically a thin wrapper around
[`tidyxl`](https://github.com/nacnudus/tidyxl) and
[`unpivotr`](https://github.com/nacnudus/unpivotr) that plots cells in their
positions and colours them by some property, e.g. number format.

```{r, echo = TRUE, fig.width = 9}
library(tidyxl)
library(tidyverse)

x <- tidy_xlsx(system.file("extdata/road-policing-driver-offence-data-jan2009-sep2006.xlsx",
                           package = "nzpullover"))

redlight <- x$data[["Red Light"]]
redlight$numFmt <- x$formats$local$numFmt[redlight$local_format_id]

ggplot(redlight, aes(col, row,
           colour = numFmt,
           alpha = is.na(content))) +
geom_point() +
scale_y_reverse() +
scale_alpha_manual(values = c(1, .5))
```
